cardinalR: Generating interesting high-dimensional data structures

### 2025-04-20 paper-cardinalR.Rmd
Added tables to different functions

@@

@@

@@

@@

>>>>

```{r}
polynomial_tb <- tibble(fun = c("gen_quadratic",
                                "gen_cubic"), 
                        exp = c("",
                                ""))
```

```{r polynomial-tb-html, eval=is_html_output()}
polynomial_tb |> 
  kable(caption = "cardinalR polynomial data generation functions", col.names = c("Function", "Explanation")) 
```

```{r polynomial-tb-pdf, eval=is_latex_output()}
polynomial_tb |> 
  kable(caption = "cardinalR polynomial data generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T)  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

@@

```{r}
pyramid_tb <- tibble(fun = c("gen_pyr",
                             "gen_pyrrect",
                             "gen_pyrtri",
                             "gen_pyrstar",
                             "gen_pyrholes"), 
                        exp = c("",
                                "",
                                "",
                                "",
                                ""))
```

```{r pyramid-tb-html, eval=is_html_output()}
pyramid_tb |> 
  kable(caption = "cardinalR pyramid data generation functions", col.names = c("Function", "Explanation")) 
```

```{r pyramid-tb-pdf, eval=is_latex_output()}
pyramid_tb |> 
  kable(caption = "cardinalR pyramid data generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T)  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

@@

```{r}
scurve_tb <- tibble(fun = c("gen_scurve",
                            "gen_scurvehole"), 
                        exp = c("",
                                ""))
```

```{r scurve-tb-html, eval=is_html_output()}
scurve_tb |> 
  kable(caption = "cardinalR S-curve data generation functions", col.names = c("Function", "Explanation")) 
```

```{r scurve-tb-pdf, eval=is_latex_output()}
scurve_tb |> 
  kable(caption = "cardinalR S-curve data generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T)  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

@@

```{r}
sphere_tb <- tibble(fun = c("gen_circle",
                            "gen_curvycycle",
                            "gen_unifsphere",
                            "gen_gridedsphere",
                            "gen_clusteredspheres"), 
                        exp = c("",
                                "",
                                "",
                                "",
                                ""))
```

```{r sphere-tb-html, eval=is_html_output()}
sphere_tb |> 
  kable(caption = "cardinalR sphere data generation functions", col.names = c("Function", "Explanation")) 
```

```{r sphere-tb-pdf, eval=is_latex_output()}
sphere_tb |> 
  kable(caption = "cardinalR sphere data generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T)  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

@@

```{r}
trigonometric_tb <- tibble(fun = c("gen_crescent",
                            "gen_curvycylinder",
                            "gen_sphericalspiral",
                            "gen_helicalspiral",
                            "gen_conicspiral",
                            "gen_nonlinear"), 
                        exp = c("",
                                "",
                                "",
                                "",
                                "",
                                ""))
```

```{r trigonometric-tb-html, eval=is_html_output()}
trigonometric_tb |> 
  kable(caption = "cardinalR trigonometric data generation functions", col.names = c("Function", "Explanation")) 
```

```{r trigonometric-tb-pdf, eval=is_latex_output()}
trigonometric_tb |> 
  kable(caption = "cardinalR trigonometric data generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T)  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```
